### 2018-01-30 submission/manuscript.Rmd
update figure legends

**Figure 1: $\alpha$-Diversity Differences between Control, Adenoma, and Carcinoma Across Sampling Site.** A) $\alpha$-diversity metric differences by group in stool samples. B) $\alpha$-diversity metric differences by group in unmatched tissue samples. C) $\alpha$-diversity metric differences by group in matched tissue samples. The dashed line represents a Z-score of 0 or no difference from the median.

**Figure 2: Relative Risk for Adenoma or Carcinoma based on $\alpha$-Diversity Metrics in Stool.** A) $\alpha$-metric relative risk for adenoma. B) $\alpha$-metric relative risk for carcinoma. Colors represent the different variable regions used within the respective study.

@@

**Figure S1: Relative Risk for Adenoma or Carcinoma based on $\alpha$-Diversity Metrics in Tissue.** A) $\alpha$-metric relative risk for adenoma. B) $\alpha$-metric relative risk for carcinoma. Colors represent the different variable regions used within the respective study.

>>>>

**Figure 1: Community Differences between Control, Adenoma, and Carcinoma Across Sampling Site.** A) Stool sample community differences by disease group. B) Unmatched tissue samples differences by disease group. C) Matched tissue sample differences by group disease group. The dashed line represents a Z-score of 0 or no difference from the median.

**Figure 2: Relative Risk for Adenoma or Carcinoma based on Bacterial Community Metrics in Stool.** A) Community-based relative risk for adenoma. B) Community-based relative risk for carcinoma. Colors represent the different variable regions used within the respective study.

@@

**Figure S1: Relative Risk for Adenoma or Carcinoma based on Bacterial Community Metrics in Tissue.** A) Community-based relative risk for adenoma. B) Community-based relative risk for carcinoma. Colors represent the different variable regions used within the respective study.

### 2018-01-30 submission/manuscript.tex
update figure legends

\hypertarget{ref-arthur_intestinal_2012}{}
5. Arthur JC, Perez-Chanona E, Mühlbauer M, Tomkovich S, Uronis JM, Fan
T-J, et al. Intestinal inflammation targets cancer-inducing activity of
the microbiota. Science (New York, N.Y.). 2012;338:120--3.

@@

\hypertarget{ref-zackular_human_2014}{}
34. Zackular JP, Rogers MAM, Ruffin MT, Schloss PD. The human gut
microbiome as a screening tool for colorectal cancer. Cancer Prevention
Research (Philadelphia, Pa.). 2014;7:1112--21.

\hypertarget{ref-schloss_introducing_2009}{}
35. Schloss PD, Westcott SL, Ryabin T, Hall JR, Hartmann M, Hollister
EB, et al. Introducing mothur: Open-Source, Platform-Independent,
Community-Supported Software for Describing and Comparing Microbial
Communities. Appl.Environ.Microbiol. {[}Internet{]}. 2009 {[}cited 12AD
Jan 1{]};75:7537--41. Available from:
\url{http://aem.asm.org/cgi/content/abstract/75/23/7537}

@@

\textbf{Figure 1: \(\alpha\)-Diversity Differences between Control,
Adenoma, and Carcinoma Across Sampling Site.} A) \(\alpha\)-diversity
metric differences by group in stool samples. B) \(\alpha\)-diversity
metric differences by group in unmatched tissue samples. C)
\(\alpha\)-diversity metric differences by group in matched tissue
samples. The dashed line represents a Z-score of 0 or no difference from
the median.

\textbf{Figure 2: Relative Risk for Adenoma or Carcinoma based on
\(\alpha\)-Diversity Metrics in Stool.} A) \(\alpha\)-metric relative
risk for adenoma. B) \(\alpha\)-metric relative risk for carcinoma.
Colors represent the different variable regions used within the
respective study.

@@

\textbf{Figure S1: Relative Risk for Adenoma or Carcinoma based on
\(\alpha\)-Diversity Metrics in Tissue.} A) \(\alpha\)-metric relative
risk for adenoma. B) \(\alpha\)-metric relative risk for carcinoma.
Colors represent the different variable regions used within the
respective study.

>>>>

\hypertarget{ref-arthur_intestinal_2012}{}
5. Arthur JC, Perez-Chanona E, Mühlbauer M, Tomkovich S, Uronis JM, Fan
T-J, et al. Intestinal inflammation targets cancer-inducing activity of
the microbiota. Science (New York, NY). 2012;338:120--3.

@@

\hypertarget{ref-zackular_human_2014}{}
34. Zackular JP, Rogers MAM, Ruffin MT, Schloss PD. The human gut
microbiome as a screening tool for colorectal cancer. Cancer Prevention
Research (Philadelphia, Pa). 2014;7:1112--21.

\hypertarget{ref-schloss_introducing_2009}{}
35. Schloss PD, Westcott SL, Ryabin T, Hall JR, Hartmann M, Hollister
EB, et al. Introducing mothur: Open-Source, Platform-Independent,
Community-Supported Software for Describing and Comparing Microbial
Communities. ApplEnvironMicrobiol {[}Internet{]}. 2009 {[}cited 12AD Jan
1{]};75:7537--41. Available from:
\url{http://aem.asm.org/cgi/content/abstract/75/23/7537}

@@

\textbf{Figure 1: Community Differences between Control, Adenoma, and
Carcinoma Across Sampling Site.} A) Stool sample community differences
by disease group. B) Unmatched tissue samples differences by disease
group. C) Matched tissue sample differences by group disease group. The
dashed line represents a Z-score of 0 or no difference from the median.

\textbf{Figure 2: Relative Risk for Adenoma or Carcinoma based on
Bacterial Community Metrics in Stool.} A) Community-based relative risk
for adenoma. B) Community-based relative risk for carcinoma. Colors
represent the different variable regions used within the respective
study.

@@

\textbf{Figure S1: Relative Risk for Adenoma or Carcinoma based on
Bacterial Community Metrics in Tissue.} A) Community-based relative risk
for adenoma. B) Community-based relative risk for carcinoma. Colors
represent the different variable regions used within the respective
study.
